---
output: github_document
---

# `forecast463` Overview 

This package is created to allow students to submit their daily forecasts for the PSU STAT 463 projects. The main function consists in the `send_prediction` which takes the following inputs:

* `group`: the number of your group which should be an integer between 1 and 17.
* `prediction`: the list object described in the "Project Description" document posted in the Piazza course page (under "Resources").
* `from`:  your group email address in the correct format (e.g. `"psu.forecasting.group.2@gmail.com"`).
* `key`: the character string representing the unique key assigned to your group which you received by email.

Here is a stylized example of the usage of the function `send_prediction`:


```{r, eval=FALSE}
group = 2
from = "psu.forecasting.group.2@gmail.com"
key = "aaaaaaaaaaaaaaa" 
send_prediction(group = group, prediction = prediction, from = from, key = key)
```

## Install Instructions

To install the `forecast463` package, please run the following code:

```{r, eval = F}
devtools::install_github("SMAC-Group/forecast463")
```
