---
output: github_document
---

```{r, echo=FALSE}
library(forecast463)
```

# `forecast463` Overview 

This package is created to allow students to submit their daily forecasts for the PSU STAT 463 projects. The main function consists in the `send_prediction` which takes the following inputs:

* `group`: the number of your group which should be an integer between 1 and 17.
* `prediction`: the list object described in the "Project Description" document posted in the Piazza course page (under "Resources").
* `from`:  your group email address in the correct format (e.g. `"psu.forecasting.group.2@gmail.com"`).
* `key`: the character string representing the unique key assigned to your group which you received by email.

Here is a stylized example of the usage of the function `send_prediction`:

```{r, eval=FALSE}
group = 2
from = "psu.forecasting.group.2@gmail.com"
key = "aaaaaaaaaaaaaaa" 
send_prediction(group = group, prediction = prediction, from = from, key = key)
```

Another available function is the `check_credential` function which is used within the previous `send_prediction` function. This function can be used to check if the credentials you will use to submit the forecast are valid (i.e. your group number, key and email address). An example of how to use this function can be found below.

```{r}
group = 2
from = "psu.forecasting.group.2@gmail.com"
key = "aaaaaaaaaaaaaaa"
credential_OK = check_credentials(group = group, from = from, key = key)
credential_OK
```

Finally, you can also check if your prediction is correctly formatted. An example prediction object can be built as follows (note: this does not represent an actual predicition since it is a random generation of numbers).

```{r}
mobile_pred = rnorm(1)
mobile_ci = mobile_pred + c(cbind(-abs(rnorm(1)), abs(rnorm(1)))) #
mobile_forecasts = list(mobile_pred = mobile_pred, mobile_ci = mobile_ci)
  
desktop_pred = rnorm(1)
desktop_ci = desktop_pred + c(cbind(-abs(rnorm(1)), abs(rnorm(1)))) 
desktop_forecasts = list(desktop_pred = desktop_pred, desktop_ci = desktop_ci)
  
silvio_pred = rnorm(1) 
silvio_ci = silvio_pred + c(-abs(rnorm(1)), abs(rnorm(1))) 
silvio_forecasts = list(silvio_pred = silvio_pred, silvio_ci = silvio_ci)
  
beyonce_pred = rnorm(1)
beyonce_ci = beyonce_pred + c(-abs(rnorm(1)), abs(rnorm(1)))
beyonce_forecasts = list(beyonce_pred = beyonce_pred, beyonce_ci = beyonce_ci)
  
chomsky_pred = rnorm(1) 
chomsky_ci = chomsky_pred + c(-abs(rnorm(1)), abs(rnorm(1)))
chomsky_forecasts = list(chomsky_pred = chomsky_pred, chomsky_ci = chomsky_ci)
  
lazio_pred = rnorm(1) 
lazio_ci = lazio_pred + c(-abs(rnorm(1)), abs(rnorm(1))) 
lazio_forecasts = list(lazio_pred = lazio_pred, lazio_ci = lazio_ci)
  
thanks_pred = rnorm(1) 
thanks_ci = thanks_pred + c(-abs(rnorm(1)), abs(rnorm(1))) 
thanks_forecasts = list(thanks_pred = thanks_pred, thanks_ci = thanks_ci)
  
 
prediction = list(mobile = mobile_forecasts,
                  desktop = desktop_forecasts, 
                  silvio = silvio_forecasts, 
                  beyonce = beyonce_forecasts, 
                  chomsky = chomsky_forecasts, 
                  lazio = lazio_forecasts, 
                  thanks = thanks_forecasts)
```

Once this prediction object is built, you can check if it is correctly formatted by using the `check_prediction` function as follows.

```{r}
prediction_OK = check_prediction(prediction = prediction)
prediction_OK
```


## Install Instructions

To install the `forecast463` package, please run the following code:

```{r, eval = F}
devtools::install_github("SMAC-Group/forecast463")
```
